Empirical Evaluation of eval in R

### 2020-08-26 inst/analysis/analysis_stable.Rmd
More data on ast size

@@

ggsave(path(PLOT_DIR, "ast_sizes.pdf"))
```

>>>>

What are the most used caller functions?

```{r caller_functions_used}
caller_function_ranked <- eval_calls %>% count(caller_function, wt = nb_ev_calls, sort = TRUE) %>% mutate(proportion = n / sum(n))

caller_function_ranked %>% datatable()

The most used function is `r caller_function_ranked[1, "caller_function"][[1]]`, as much as `r 100 * caller_function_ranked[1, "proportion"][[1]]`%.

```{r match_arg}
match_arg_r <- caller_function_ranked %>% filter(caller_function == "match.arg")

r("match arg number", match_arg_r[1, "n"][[1]])
r("match arg percent", percent(match_arg_r[1, "proportion"][[1]]))
```

@@

ggsave(path(PLOT_DIR, "ast_sizes.pdf"))

ast_sizes_prop <- ast_sizes %>% count(expr_resolved_ast_size, wt = nb_eval_calls) %>%
                      arrange(desc(expr_resolved_ast_size)) %>% 
                      mutate(proportion = n / nb_eval_calls) %>% 
                      mutate(cumulative = cumsum(proportion))

ast_size_one <- ast_sizes %>% filter(expr_resolved_ast_size == 1) 
nb_ast_size_one <- count(ast_size_one, wt = nb_ev_calls)$n
nb_ast_size_one_call_sites <- nb_eval_call_sites(ast_size_one)
r("nb ast one percent", ratio(nb_ast_size_one, nb_eval_calls))
r("nb ast one call site percent", ratio(nb_ast_size_one_call_sites, nb_call_sites))

nb_nodes_many <- ast_sizes_prop %>% filter(cumulative >= 95) %>% .[1,]

r("ast size 95", nb_nodes_many$expr_resolved_ast_size)
r("ast size 95 exact percent", percent(nb_nodes_many$proportion))
